\section*{|| Technical skills ||}
\begin{itemize}
	\item I have been programming in C and C++ for almost 3 years professionally and 7 years on my spare time as an enthuastic hobby programmer. I aim for simplicity, safety and speed when programming. Fairly good understanding of assembly language (x86-64). Thorough experience integrating and using libraries, such as LLVM, GLFW, Dear ImGUI, STB single-header libraries, sokol, meshoptimizer, Volk, Raylib, Qt, Expat, JSMN...
	
	\item Comfortable in both command-line and graphical environments and qualified in systems programming, both Windows (Batch, Win32) and Unix (Bash, POSIX).
	
	\item Fond of data-oriented programming. You have to know the platform and the data you are working with in order to obtain the solution of your problem. Passion for computer architecture and hardware understanding in order to get the most out of it. Object-oriented design understanding. Professional experience in both of them.
	
	\item Compiler engineering experience developing several toy programming languages with a tendency to restrict dependencies, own the code and respect compile times.
	
	\item Very brief personal experience with low-level graphics APIs, such as Vulkan, OpenGL and DirectX (11, 12), having practiced more with the open-source ones. Fairly good understanding of game engines and the GPU pipeline.
	
	\item Fairly in-depth understanding of how an operating system kernel works, performance constraints and hardware-software interaction details. Developed some operating system kernels from scratch with very primitive functionality.
	
	\item Expertise working with files, parsing and generating them, both text and binary formats.
	
	\item Language interoperability based on the C ABI. Binding creation to interoperate between C, C++, Objective-C, Rust and Zig. More than decent understanding of how linkers work.
	
	\item API design and project organization.
	
	\item Use of build systems like CMake, MSBuild, Makefile, Zig Build, Maven and Ant, both professionally and personally.
	
	\item Use of version control systems such as Git, Perforce or CVS, both professionally and personally.
	
	\item Experience with other programming languages, like Zig, Java, Rust and Python.
\end{itemize}